\pagestyle{empty}
\addcontentsline{toc}{chapter}{Literatūra}
\section*{Literatūra}

\subsubsection{Bendra}

\begin{itemize}
    \opt{color}{\item \url{http://www.mathlinks.ro} \quad (olimpiadinės
    matematikos forumas)}
    \opt{BW}{\item http://www.mathlinks.ro \quad (olimpiadinės
    matematikos forumas)}
    \opt{color}{\item \url{http://www.math.ca/crux/} \quad (olimpiadinės
    matematikos žurnalas)}
    \opt{BW}{\item http://www.math.ca/crux/ \quad (olimpiadinės
    matematikos žurnalas)}
    \opt{color}{\item \url{http://www.math.ust.hk/excalibur/} \quad
    (olimpiadinės matematikos žurnalas)}
    \opt{BW}{\item http://www.math.ust.hk/excalibur/ \quad
    (olimpiadinės matematikos žurnalas)}
  \item Arthur Engel, \emph{Problem Solving Strategies}, Springer, 1998.
  \item Paul Zeitz, \emph{Art and Craft of Problem Solving}, Wiley, 2007.
  \item D. Djukic, V. Jankovic, I. Matic, N.Petrovic, \emph{The IMO
    Compendium}, Springer, 2006.
\end{itemize}


\subsubsection{Skaičių teorija}

\begin{itemize}
    \opt{color}{\item \url{http://www.mathlinks.ro/index.php?f=456} \quad(Problems in Elementary
    Number theory (PEN))}
    \opt{BW}{\item http://www.mathlinks.ro/index.php?f=456 \quad(Problems in Elementary
    Number theory (PEN))}
  \item T. Andreescu, D. Andrica, Z. Feng, \emph{104 Number Theory
    Problems}, Birkhauser, 2007.
  \item T. Andreescu, D. Andrica, \emph{An Introduction to Diophantine
    Equations}, GIL, 2002.
  \item K. Ireland, M. Rosen, \emph{A Classical Introduction to Modern
    Number Theory}, Springer, 1990.
\end{itemize}

\subsubsection{Algebra}

\begin{itemize}
  \item Pham Kim Hung, \emph{Secrets in Inequalities (Volume 1)}, GIL
    Publishing House, 2007.
  \item Samin Riasat, \emph{Basics of Olympiad Inequalities}, 2008.
  \item Ivan Matic, \emph{Classical Inequalities}, The IMO Compendium
    Group, 2007.
  \item Hojoo Lee, \emph{Topics in Inequalities - Theorems and
    Techniques}, 2007.
  \item Tran Phuong, \emph{Diamonds in Mathematical Inequalities},
    Hanoi Publishing House, 2007.
\opt{color}{\item Thomas J. Mildorf, \emph{Olympiad Inequalities}, 2006.\\
    (\url{http://www.artofproblemsolving.com/Resources/Papers/MildorfInequalities.pdf})}
\opt{BW}{\item Thomas J. Mildorf, \emph{Olympiad Inequalities}, 2006.\\
    (http://www.artofproblemsolving.com/Resources/Papers/MildorfInequalities.pdf)}
  \item T. Andreescu, V. Cartoaje, G. Dospinescu, M. Lascu, \emph{Old
    and New Inequalities}, GIL Publishing House, 2003.
  \item J. Michael Steele, \emph{The Cauchy-Schwarz Master Class},
    Cambridge University Press, 2004.
\end{itemize}

\subsubsection{Kombinatorika}
\begin{itemize}
  \item Ted Alper, \emph{Two Player Games in Olympiads and Real Life},
    Berkeley Math Circle, 2000.
\end{itemize}
